### 2022-08-12 notes lisa/notes.tex
include graphs for data from conditionals

>>>>

\section{Experiments with Condstionals}

	\subsection{1c---Conditional embedding,  are you sure?, assent + assertion of complement + Q-A judgment}
		\ex. \a. \textbf{Christopher:} If Cole discovered that Julian dances salsa, Logan will be joyful.
			\b. \textbf{Sandy:} Are you sure?
			\b. \textbf{Christopher:} Yes, I'm sure that Julian dances Salsa.
			\z.
		\z.

		\begin{figure}[h]
			\centering
			\includegraphics[scale=0.85]{figures/c1-correl.pdf}
			\caption{Mean not-at-issueness ratings vs mean certainty ratings by predicate, Exp. 1c}
			\label{fig:m1-corr}
		\end{figure}

	\subsection{2c---Conditional embedding yes, that's true+complement diagnostic (+ acceptability rating)} % (fold)
		\ex. \a. \textbf{Christopher:} If Cole discovered that Julian dances salsa, Logan will be joyful.
			\b. \textbf{Sandy:} Yes, that’s true, Julian dances salsa.
			\z.
		\z.

		\begin{figure}[h]
			\centering
			\includegraphics[scale=0.85]{figures/c2-correl.pdf}
			\caption{Mean not-at-issueness ratings vs mean certainty ratings by predicate, Exp. 2c}
			\label{fig:m1-corr}
		\end{figure}

	\subsection{3c---Conditional embedding, yes, that's true + negation of main clause (+ acceptability rating)} % (fold)
		\ex. \a. \textbf{Christopher:} If Cole discovered that Julian dances salsa, Logan will be joyful.
			\b. \textbf{Sandy:} Yes, that’s true, but Cole didn't discover it.
			\z.
		\z.

		\begin{figure}[h]
			\centering
			\includegraphics[scale=0.85]{figures/c3-correl.pdf}
			\caption{Mean not-at-issueness ratings vs mean certainty ratings by predicate, Exp. 3c}
			\label{fig:m1-corr}
		\end{figure}
